Review Paper Draft

### 2020-08-15 main.tex
Section 1: more edits

One method for analyzing data in the presence of correlated loci is LD pruning. LD pruning can be an important preprocessing step in a GWAS analysis, for which there exist a variety of algorithms and methods. The overarching approach of these methods is to sequentially thin SNPs, so that only SNPs correlated with each other below some desired threshold are used in modeling and testing procedures. An alternative solution to the problem of LD is the use of multivariate methods such as multiple linear regression, which adjusts for and estimates the effects of numerous variants simultaneously. However, classical approaches rely on collecting data with more observations than unknown parameters. This is typically infeasible in genome-wide studies where the number of features greatly exceeds the number of observations. Penalized regression methods make such problems tractable by constraining the solution space of coefficient estimates. The Lasso is a widely used penalized regression method \citep{tibshirani1996regression}. It relies on an assumption of sparsity, which allows coefficient estimation and variable selection to be accomplished simultaneously. It also provides considerable computational advantages that scale up well to very large data sets. These features make the Lasso attractive for the analysis of high-dimensional genetic data where identifying a list of variants most highly associated with a particular trait is often of interest.

>>>>

One method for analyzing data in the presence of correlated loci is LD pruning, which involves sequentially thinning SNPs, so that only those correlated with each other below some desired threshold are used in modeling and testing procedures. LD pruning can be an important preprocessing step in a GWAS analysis, for which there exist a variety of algorithms and methods. An alternative solution to the problem of LD is the use of multivariate methods such as multiple linear regression, which adjusts for and estimates the effects of numerous variants simultaneously. However, classical approaches rely on collecting data with more observations than unknown parameters. This is typically infeasible in genome-wide studies where the number of features greatly exceeds the number of observations. Penalized regression methods make such problems tractable by constraining the solution space of coefficient estimates. The Lasso is a widely used penalized regression method \citep{tibshirani1996regression}. It relies on an assumption of sparsity, which allows coefficient estimation and variable selection to be accomplished simultaneously. It also provides considerable computational advantages that scale up well to very large data sets. These features make the Lasso attractive for the analysis of high-dimensional genetic data where identifying a list of variants most highly associated with a particular trait is often of interest.
